---
title: "Green & Impervious Space Visuals"
author: "Francine Stephens"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: flatly
    highlight: espresso
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE,
  comment = NA
)

## LIBRARIES
packages <- c(
  "readr",
  "tidyverse",
  "sf",
  "ggplot2", 
  "ggbeeswarm",
  "ggstream",
  "scales",
  "units",
  "ggcorrplot",
  "modelsummary",
  "stargazer",
  "panelr",
  "tigris",
  "censusapi", 
  "tidycensus",
  "RColorBrewer",
  "hrbrthemes",
  "viridis", 
  "wesanderson",
  "leaflet", 
  "tmap"
)
lapply(packages, library, character.only = T)

## PATHS
setwd("~/Projects/public_space")
wd <- getwd()
green_space_path <- "/green_space/gee/"
imperv_space_path <- "/impervious_space/"
census_data_path <- "/census"
shp_repo <- "C:/Users/Franc/Documents/Shapefile_Repository"
shp2010_path <- "/2010USA_CensusGeog_Shp"
cbsa_path <- "/tl_2010_us_cbsa10/"
metdiv_path <- "/tl_2010_us_metdiv10/"
cbg10_path <- "/us_blck_grp_2010/"
places10_path <- "/tl2010_us_place_2010/"


## SHAPEFILE IMPORTS
cbg10 <- st_read(paste0(shp_repo,
                        shp2010_path,
                        cbg10_path,
                        "US_blck_grp_2010.shp"), 
                 quiet = F)

## DATA IMPORTS-----------------------------------------------------------------
full_cbg_data_l <- readRDS("all_vars_on_cbg10_LONG.rds")
full_cbg_data_chg_w <- readRDS("chg_vars_on_cbg10_WIDE.rds")


# PARAMETERS--------------------------------------------------------------------
midwest_core <- c("MI", "OH", "IN", "IL")
midwest_center <- c("WI", "MN", "MO", "KS", "NE")

```

## Data Updates

There are two issues that I found with the results that I presented. The graphics in the other sections are not fully updated from the previous meeting. 

**1. I only pulled non-tree vegetation.**

Green space composition varies quite a bit across places. In some places, tree-cover is the more prominent type of vegetation (compared to shrubs, bushes, grasses). The EVI measure does not distinguish between tree cover and other types of vegetation. After reading more papers on green space measures, I have noticed that many studies aggregate tree cover and other types of vegetation, but also call out patterns where there are differences between the various types of vegetation. 

Prior studies have often treated green space as a monolithic concept, employing only a few measures. As I read and view the raster data, I see the value of both continuous and categorical measures of green space. The spatial distributions of green spaces identified with each green measure look different. The spatial patterns of green amenities, i.e. parks, trails, golf courses and sports fields (categorical measures) are highly different from the patterns identified with general, comprehensive green measures, e.g. NDVI or percent treecover, percent other vegetation (continuous measures). Tests of spatial autocorrelation would indicate whether these differences are statistically different. 

**Steps In-progress**

* Pulled the tree cover measures. 
* Compute the change over time in % tree cover, % other vegetation, and % tree cover + % other vegetation for each pixel and use zonal statistics for the change over time measures. 
  + Computing change within pixel and then aggregating is cleaner than how I was previously computing (i.e., compute the % per year, aggregating to CBG, and then calculating the change across CBGs over time.) 
* "Check" % tree cover and % other vegetation with categorical measures (e.g., polygons of open space, NLCD categorical data.). This would pave the way for SVM classification, too. 



**2. The 2020 data have fewer satellite images available compared to the previous years.** 

The satellite had a different cadence in 2020, which is unfortunate, because I had standardized the time period snapshot for the imagery using the 2000 imagery. 

**Next steps**

I will need to reduce the imagery interval of 2000 and 2010 to be comparable to the 2020 data, unless I can find some other work-around.  



## Place-Level Graphics {.tabset .tabset-fade}

```{r line graph functions}
## green v. imperv functions 
prep_for_space_time_line_graphs <- function(x) { 
  x %>%       
   ungroup() %>% 
  filter(top100_place == 1) %>% 
  mutate(PLACE_NM = str_remove(PLACE_DERIVED_NM, " city"),
         PLACE_ST_NM = str_c(PLACE_NM, state_ab, sep = ", ")
  ) %>%  
  group_by(PLACE_ST_NM, region, wave) %>%
  summarize(impervious = sum(imperv_area),
            green = median(med_pct_veg),
            area = sum(area)
            ) %>% 
  ungroup() %>% 
  mutate(perc_impervious = (impervious/area) * 100) %>% 
  rename(perc_green = "green") %>%
  pivot_longer(
               cols = starts_with("perc_"),
               names_to = "landcover",
               values_to = "percent"
               )
}

make_imp_green_line_graphs <- function(x) { 
  x %>%  
    mutate(landcover = str_remove(landcover, "perc_")) %>%
  ggplot(aes(wave, percent, group = PLACE_ST_NM)) +
  geom_line(aes(color=PLACE_ST_NM), size = 1.2) + 
  geom_point(aes(color=PLACE_ST_NM), size = 1.5) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Share of Green and Impervious Space in Selected Cities",
    x = "Year",
    y = "% of Area",
    color = "Places") + 
  theme_minimal() + 
  facet_wrap(~ landcover)
} 

# Imperv functions by racial composition subset
create_racial_comp_for_imp_lines <- function(x) {
  x %>%  
  ungroup() %>% 
  filter(top100_place == 1) %>% 
  mutate(PLACE_NM = str_remove(PLACE_DERIVED_NM, " city"),
         PLACE_ST_NM = str_c(PLACE_NM, state_ab, sep = ", "),
         majority_minority = if_else(WHITE_NH_PCT < 50,
                                     "Majority Nonwhite",
                                     "Majority white"),
         race_comp = case_when(
           majority_minority == "Majority white" ~ "Majority white",
           BLACK_NH_PCT > 50  ~ "Majority Black",
           ASIAN_PACIFIC_NH_PCT > 50 ~ "Majority Asian",
           HISPANIC_PCT > 50 ~ "Majority Latinx",
           TRUE  ~ "No Majority"
         )
  ) %>%  
  group_by(PLACE_ST_NM, region, race_comp, wave) %>%
  summarize(impervious = sum(imperv_area),
            green = median(med_pct_veg),
            area = sum(area)
            ) %>% 
  ungroup() %>% 
  mutate(perc_impervious = (impervious/area) * 100) %>%
  rename(perc_green = "green") %>%
  pivot_longer(
               cols = starts_with("perc_"),
               names_to = "landcover",
               values_to = "percent"
               ) 
}

make_race_comp_imp_line_graph <- function(x) {
  x %>%
  ggplot(aes(wave, percent, group = race_comp)) +
  geom_line(aes(color=race_comp), size = 1.2) + 
  geom_point(aes(color=race_comp), size = 1.5) +
  scale_color_manual(values = wes_palette("Darjeeling1") 
                     ) +
  theme_minimal() + 
  labs(
    title = "Share of Impervious Space by Neighborhood Racial Composition",
    x = "Year",
    y = "% of Area",
    color = "Racial Composition") + 
    facet_wrap(~ PLACE_ST_NM)
}

```


### Northeast
```{r Northeast imperv v green}
## Northeast
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Northeast") %>% 
  make_imp_green_line_graphs(.)

```

**Impervious Space By Neighborhood Racial Composition**


```{r racial comp impervious space NE}
## NE RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Northeast" & landcover == "perc_impervious") %>%
  make_race_comp_imp_line_graph(.)

```



White neighborhoods with less impervious space than minority majority neighborhoods:

* New York, NY
* Rochester, NY.

Similar level of impervious space across all types of neighborhoods: 

* Jersey City, NJ

No racial majority trends downward:

* Boston, MA after 2010 
* Buffalo, NY after 2010 

Miscellaneous noticeable shifts:

* Boston's Latinx neighborhoods share of impervious space drops from 1990 to 2010.


### Mid-Atlantic
```{r Midatlantic imperv v green}
## Mid-Atlantic
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Mid-Atlantic") %>% 
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition**


```{r racial comp impervious space Midatl}
## Mid-Atl RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Mid-Atlantic" & landcover == "perc_impervious") %>% 
  make_race_comp_imp_line_graph(.)

```



White neighborhoods with less built up space than minority majority neighborhoods:

* Chesapeake, VA
* Virginia Beach, VA

Declining impervious space among neighborhoods with no racial/ethnic majority: 

* Philadelphia, PA
* Pittsburgh, PA
* Washington, DC
* Chesapeake, VA

Increasing impervious space among neighborhoods with no racial/ethnic majority:

* Baltimore, MD
* Norfolk, VA
* Virginia Beach, VA

White neighborhoods with growing amounts of impervious space: 

* Pittsburgh
* DC


### Midwest
```{r Midwest imperv v green core}
## Midwest core
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>% 
  mutate(state_ab = str_extract(PLACE_ST_NM, "[^, ]+$"), 
         PLACE_ST_NM = str_replace(PLACE_ST_NM, " \\s*\\([^\\)]+\\)", "")) %>%
  filter(region == "Midwest" & state_ab %in% midwest_core) %>% 
  make_imp_green_line_graphs(.)

```

```{r Midwest imperv v green center}
## Midwest center
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>% 
  mutate(state_ab = str_extract(PLACE_ST_NM, "[^, ]+$"), 
         PLACE_ST_NM = str_replace(PLACE_ST_NM, " \\s*\\([^\\)]+\\)", "")) %>%
  filter(region == "Midwest" & state_ab %in% midwest_center) %>% 
  make_imp_green_line_graphs(.)

```

**Impervious Space By Neighborhood Racial Composition** 

```{r racial comp impervious space Midwest core}
## Midwest RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  mutate(state_ab = str_extract(PLACE_ST_NM, "[^, ]+$"),
         PLACE_ST_NM = str_replace(PLACE_ST_NM, " \\s*\\([^\\)]+\\)", "")) %>%
  filter(region == "Midwest" & state_ab %in% midwest_core & landcover == "perc_impervious") %>% 
  make_race_comp_imp_line_graph(.)

```

```{r racial comp impervious space Midwest central}
## Midwest RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  mutate(state_ab = str_extract(PLACE_ST_NM, "[^, ]+$")
        ) %>%
  filter(region == "Midwest" & state_ab %in% midwest_center & landcover == "perc_impervious") %>% 
  make_race_comp_imp_line_graph(.)

```

White neighborhoods with less impervious space than minority majority neighborhoods: 

* Fort Wayne, IN 
* Indianapolis, IN
* Kansas City, MO
* Lincoln, NE (to a lesser extent)
* Toledo, OH (to a lesser extent)

Similar level of impervious space across all types of neighborhoods: 

* Chicago, IL
* Cleveland, OH

Minority neighborhood with less impervious space than white majority neighborhoods:

* Detroit, MI (Black)
* Wichita, KS (Black)

Neighborhoods without a majority racial group have least amount of impervious space:

* St. Louis, MO
* Wichita, KS


### South
```{r South imperv v green}
## South
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "South") %>% 
  mutate(PLACE_ST_NM = str_remove(PLACE_ST_NM, " urban county"), 
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " government"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metropolitan"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metro"),
         PLACE_ST_NM = gsub("\\s*\\([^\\)]+\\)", "", PLACE_ST_NM)
         ) %>%
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition**

```{r racial comp impervious space south}
## South RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "South" & landcover == "perc_impervious") %>% 
  mutate(PLACE_ST_NM = str_remove(PLACE_ST_NM, " urban county"), 
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " government"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metropolitan"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metro"),
         PLACE_ST_NM = gsub("\\s*\\([^\\)]+\\)", "", PLACE_ST_NM)
         ) %>%
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods:

* Baton Rouge, LA
* Greensboro, NC
* Jacksonville, FL
* Louisville, KY 
* Miami (?)


### Southwest  

```{r Southwest imperv v green}
## Southwest
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Southwest") %>% 
  make_imp_green_line_graphs(.)

```

**Impervious Space By Neighborhood Racial Composition**  

```{r racial comp impervious space southwest}
## Southwest RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Southwest" & landcover == "perc_impervious") %>% 
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods:

* Oklahoma City, OK
* Scottsdale, AZ
* Corpus Christi (?)


**Bexar County, TX: County Seat: San Antonio, TX**
```{r bexar areal space prep}
bexar_all_data <- full_cbg_data_l %>% 
  ungroup() %>% 
  filter(state_co == "48029")

bexar_shp <- cbg10 %>%
  select(GEOID10, STATEFP10, COUNTYFP10) %>% 
  right_join(bexar_all_data, by ="GEOID10") 

```

```{r bexar impervious}
tm_shape(bexar_shp) +
  tm_polygons("perc_imperv", 
              style="quantile", 
              palette="Greys",
              title="Bexar County Impervious Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")

```

```{r bexar median pct veg}
tm_shape(bexar_shp) +
  tm_polygons("med_pct_veg", 
              style="quantile", 
              palette="Greens",
              title="Median % Green Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")

```  

```{r bexar evi pct green}
#green_bexar_evi <- 
  tm_shape(bexar_shp) +
  tm_polygons("perc_green", 
              style="quantile", 
              palette="Greens",
              title="Green Space by EVI",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")

```



### Mountain West
```{r West imperv v green}
## West
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "West") %>% 
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition**

```{r racial comp impervious space mountain}
## Mountain RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "West" & landcover == "perc_impervious") %>% 
  make_race_comp_imp_line_graph(.)

```


### Pacific West
```{r Pacific imperv v green}
## Pacific
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Pacific" & PLACE_ST_NM != "Anchorage municipality, AK") %>% 
  make_imp_green_line_graphs(.)
```



```{r racial comp impervious space Pacific}
## PACIFIC RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Pacific" & PLACE_ST_NM != "Anchorage municipality, AK") %>% 
  filter(landcover == "perc_impervious") %>% 
  mutate(PLACE_ST_NM = str_remove(PLACE_ST_NM, "Urban ")) %>%
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods:

* Anaheim, CA
* Los Angeles, CA (?)  



<p>&nbsp;</p>


## Metro-level Graphics

**SA, TX METRO** 
```{r sa metro prep}
satx_metro <- full_cbg_data_l %>% 
  ungroup() %>% 
  filter(cbsacode == "41700")

satx_metro_shp <- cbg10 %>%
  select(GEOID10, STATEFP10, COUNTYFP10) %>% 
  right_join(satx_metro, by ="GEOID10") 

```


```{r sa metro imperv space} 
tm_shape(satx_metro_shp) +
  tm_polygons("perc_imperv", 
              style="quantile", 
              palette = "Greys",
              title="Impervious Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")
```


```{r sa metro median veg space} 
tm_shape(satx_metro_shp) +
  tm_polygons("med_pct_veg", 
              style="quantile", 
              palette = "Greens",
              title="Median % Green Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")
```

```{r sa metro median green space} 
tm_shape(satx_metro_shp) +
  tm_polygons("perc_green", 
              style="quantile", 
              palette = "Greens",
              title="Green Space by EVI",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")
```

