---
title: "Green & Impervious Space Visuals"
author: "Francine Stephens"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: flatly
    highlight: espresso
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE,
  comment = NA
)

## LIBRARIES
packages <- c(
  "readr",
  "tidyverse",
  "sf",
  "ggplot2", 
  "ggbeeswarm",
  "ggstream",
  "scales",
  "units",
  "ggcorrplot",
  "modelsummary",
  "stargazer",
  "panelr",
  "tigris",
  "censusapi", 
  "tidycensus",
  "RColorBrewer",
  "hrbrthemes",
  "viridis", 
  "wesanderson",
  "leaflet", 
  "tmap"
)
lapply(packages, library, character.only = T)

## PATHS
setwd("~/Projects/public_space")
wd <- getwd()
green_space_path <- "/green_space/gee/"
imperv_space_path <- "/impervious_space/"
census_data_path <- "/census"
shp_repo <- "C:/Users/Franc/Documents/Shapefile_Repository"
shp2010_path <- "/2010USA_CensusGeog_Shp"
cbsa_path <- "/tl_2010_us_cbsa10/"
metdiv_path <- "/tl_2010_us_metdiv10/"
cbg10_path <- "/us_blck_grp_2010/"
places10_path <- "/tl2010_us_place_2010/"


## SHAPEFILE IMPORTS
cbg10 <- st_read(paste0(shp_repo,
                        shp2010_path,
                        cbg10_path,
                        "US_blck_grp_2010.shp"), 
                 quiet = F)

## DATA IMPORTS-----------------------------------------------------------------
full_cbg_data_l <- readRDS("all_vars_on_cbg10_LONG.rds")
full_cbg_data_chg_w <- readRDS("chg_vars_on_cbg10_WIDE.rds")

```

## Place-Level Graphics {.tabset .tabset-fade}

```{r line graph functions}
## green v. imperv functions 
prep_for_space_time_line_graphs <- function(x) { 
  x %>%       
   ungroup() %>% 
  filter(top100_place == 1) %>% 
  mutate(PLACE_NM = str_remove(PLACE_DERIVED_NM, " city"),
         PLACE_ST_NM = str_c(PLACE_NM, state_ab, sep = ", ")
  ) %>%  
  group_by(PLACE_ST_NM, region, wave) %>%
  summarize(impervious = sum(imperv_area),
            green = median(med_pct_veg),
            area = sum(area)
            ) %>% 
  ungroup() %>% 
  mutate(perc_imperv = (impervious/area) * 100) %>% 
  rename(perc_green = "green") %>%
  pivot_longer(
               cols = starts_with("perc_"),
               names_to = "landcover",
               values_to = "percent"
               )
}

make_imp_green_line_graphs <- function(x) { 
  x %>% 
  ggplot(aes(wave, percent, group = PLACE_ST_NM)) +
  geom_line(aes(color=PLACE_ST_NM), size = 1.2) + 
  geom_point(aes(color=PLACE_ST_NM), size = 1.5) +
  scale_color_brewer(palette = "Set2") +
  labs(
    title = "Share of Green and Impervious Space in Selected Cities",
    x = "Year",
    y = "% of Area",
    color = "Places") + 
  ggthemes::theme_fivethirtyeight() + 
  #theme_light() + 
  facet_wrap(~ landcover) 
} 

# Imperv functions by racial composition subset
create_racial_comp_for_imp_lines <- function(x) {
  x %>%  
  ungroup() %>% 
  filter(top100_place == 1) %>% 
  mutate(PLACE_NM = str_remove(PLACE_DERIVED_NM, " city"),
         PLACE_ST_NM = str_c(PLACE_NM, state_ab, sep = ", "),
         majority_minority = if_else(WHITE_NH_PCT < 50,
                                     "Majority Nonwhite",
                                     "Majority white"),
         race_comp = case_when(
           majority_minority == "Majority white" ~ "Majority white",
           BLACK_NH_PCT > 50  ~ "Majority Black",
           ASIAN_PACIFIC_NH_PCT > 50 ~ "Majority Asian",
           HISPANIC_PCT > 50 ~ "Majority Latinx",
           TRUE  ~ "No Majority"
         )
  ) %>%  
  group_by(PLACE_ST_NM, region, race_comp, wave) %>%
  summarize(impervious = sum(imperv_area),
            green = median(med_pct_veg),
            area = sum(area)
            ) %>% 
  ungroup() %>% 
  mutate(perc_imperv = (impervious/area) * 100) %>%
  rename(perc_green = "green") %>%
  pivot_longer(
               cols = starts_with("perc_"),
               names_to = "landcover",
               values_to = "percent"
               ) 
}

make_race_comp_imp_line_graph <- function(x) {
  x %>%
  ggplot(aes(wave, percent, group = race_comp)) +
  geom_line(aes(color=race_comp), size = 1.2) + 
  geom_point(aes(color=race_comp), size = 1.5) +
  scale_color_manual(values = wes_palette("Darjeeling1") 
                     ) +
  ggthemes::theme_fivethirtyeight() + 
  #theme_light() + 
  labs(
    title = "Share of Impervious Space by Neighborhood Racial Composition",
    x = "Year",
    y = "% of Area",
    color = "Racial Composition") + 
    facet_wrap(~ PLACE_ST_NM)
}

```


### Northeast
```{r Northeast imperv v green}
## Northeast
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Northeast") %>% 
  make_imp_green_line_graphs(.)

```

**Impervious Space By Neighborhood Racial Composition**


```{r racial comp impervious space NE}
## NE RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Northeast" & landcover == "perc_imperv") %>% 
  make_race_comp_imp_line_graph(.)

```



White neighborhoods with less impervious space than minority majority neighborhoods:

* New York, NY
* Rochester, NY.

Similar level of impervious space across all types of neighborhoods: 

* Jersey City, NJ

No racial majority trends downward:

* Boston, MA after 2010 
* Buffalo, NY after 2010 

Miscellaneous noticeable shifts:

* Boston's Latinx neighborhoods share of impervious space drops from 1990 to 2010.


### Mid-Atlantic
```{r Midatlantic imperv v green}
## Mid-Atlantic
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Mid-Atlantic") %>% 
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition**


```{r racial comp impervious space Midatl}
## Mid-Atl RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Mid-Atlantic" & landcover == "perc_imperv") %>% 
  make_race_comp_imp_line_graph(.)

```



White neighborhoods with less built up space than minority majority neighborhoods:

* Chesapeake, VA
* Virginia Beach, VA

Declining impervious space among neighborhoods with no racial/ethnic majority: 

* Philadelphia, PA
* Pittsburgh, PA
* Washington, DC
* Chesapeake, VA

Increasing impervious space among neighborhoods with no racial/ethnic majority:

* Baltimore, MD
* Norfolk, VA
* Virginia Beach, VA

White neighborhoods with growing amounts of impervious space: 

* Pittsburgh
* DC


### Midwest
```{r Midwest imperv v green}
## Midwest
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Midwest") %>% 
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition** 

```{r racial comp impervious space Midwest}
## Midwest RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Midwest" & landcover == "perc_imperv") %>% 
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods: 

* Fort Wayne, IN 
* Indianapolis, IN
* Kansas City, MO
* Lincoln, NE (to a lesser extent)
* Toledo, OH (to a lesser extent)

### South
```{r South imperv v green}
## South
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "South") %>% 
  mutate(PLACE_ST_NM = str_remove(PLACE_ST_NM, " urban county"), 
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " government"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metropolitan"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metro"),
         PLACE_ST_NM = gsub("\\s*\\([^\\)]+\\)", "", PLACE_ST_NM)
         ) %>%
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition**

```{r racial comp impervious space south}
## South RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "South" & landcover == "perc_imperv") %>% 
  mutate(PLACE_ST_NM = str_remove(PLACE_ST_NM, " urban county"), 
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " government"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metropolitan"),
         PLACE_ST_NM = str_remove(PLACE_ST_NM, " metro"),
         PLACE_ST_NM = gsub("\\s*\\([^\\)]+\\)", "", PLACE_ST_NM)
         ) %>%
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods:

* Baton Rouge, LA
* Greensboro, NC
* Jacksonville, FL
* Louisville, KY 
* Miami (?)


### Southwest  

```{r Southwest imperv v green}
## Southwest
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Southwest") %>% 
  make_imp_green_line_graphs(.)

```

**Impervious Space By Neighborhood Racial Composition**  

```{r racial comp impervious space southwest}
## Southwest RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Southwest" & landcover == "perc_imperv") %>% 
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods:

* Oklahoma City, OK
* Scottsdale, AZ
* Corpus Christi (?)


**Bexar County, TX: County Seat: San Antonio, TX**
```{r bexar areal space prep}
bexar_all_data <- full_cbg_data_l %>% 
  ungroup() %>% 
  filter(state_co == "48029")

bexar_shp <- cbg10 %>%
  select(GEOID10, STATEFP10, COUNTYFP10) %>% 
  right_join(bexar_all_data, by ="GEOID10") 

```

```{r bexar impervious}
tm_shape(bexar_shp) +
  tm_polygons("perc_imperv", 
              style="quantile", 
              palette="Greys",
              title="Bexar County Impervious Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")

```

```{r bexar median pct veg}
tm_shape(bexar_shp) +
  tm_polygons("med_pct_veg", 
              style="quantile", 
              palette="Greens",
              title="Median % Green Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")

```  

```{r bexar evi pct green}
#green_bexar_evi <- 
  tm_shape(bexar_shp) +
  tm_polygons("perc_green", 
              style="quantile", 
              palette="Greens",
              title="Green Space by EVI",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")

```



### Mountain West
```{r West imperv v green}
## West
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "West") %>% 
  make_imp_green_line_graphs(.)

```


**Impervious Space By Neighborhood Racial Composition**

```{r racial comp impervious space mountain}
## Mountain RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "West" & landcover == "perc_imperv") %>% 
  make_race_comp_imp_line_graph(.)

```


### Pacific West
```{r Pacific imperv v green}
## Pacific
full_cbg_data_l %>%
  prep_for_space_time_line_graphs(.) %>%
  filter(region == "Pacific" & PLACE_ST_NM != "Anchorage municipality, AK") %>% 
  make_imp_green_line_graphs(.)
```



```{r racial comp impervious space Pacific}
## PACIFIC RACE & IMPERVIOUS SPACE
full_cbg_data_l %>%  
  create_racial_comp_for_imp_lines(.) %>% 
  filter(region == "Pacific" & PLACE_ST_NM != "Anchorage municipality, AK") %>% 
  filter(landcover == "perc_imperv") %>% 
  mutate(PLACE_ST_NM = str_remove(PLACE_ST_NM, "Urban ")) %>%
  make_race_comp_imp_line_graph(.)

```


White neighborhoods with less built up space than minority majority neighborhoods:

* Anaheim, CA
* Los Angeles, CA (?)  



***


## Metro-level Graphics

**SA, TX METRO** 
```{r sa metro prep}
satx_metro <- full_cbg_data_l %>% 
  ungroup() %>% 
  filter(cbsacode == "41700")

satx_metro_shp <- cbg10 %>%
  select(GEOID10, STATEFP10, COUNTYFP10) %>% 
  right_join(satx_metro, by ="GEOID10") 

```


```{r sa metro imperv space} 
tm_shape(satx_metro_shp) +
  tm_polygons("perc_imperv", 
              style="quantile", 
              palette = "Greys",
              title="Impervious Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")
```


```{r sa metro median veg space} 
tm_shape(satx_metro_shp) +
  tm_polygons("med_pct_veg", 
              style="quantile", 
              palette = "Greens",
              title="Median % Green Space",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")
```

```{r sa metro median green space} 
tm_shape(satx_metro_shp) +
  tm_polygons("perc_green", 
              style="quantile", 
              palette = "Greens",
              title="Green Space by EVI",
              border.alpha = 0.2) + 
      tm_facets(by = "wave")
```

