---
title: "Accessibility of Parks"
author: "Francine Stephens"
date: "6/20/2021"
date: "Last Updated: `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: journal
    highlight: espresso
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE,
  warning = FALSE,
  comment = NA
  )

## LIBRARIES
packages <- c(
  "readr",
  "tidyverse",
  "sf",
  "ggplot2", 
  "scales",
  "units",
  "ggcorrplot",
  "modelsummary",
  "stargazer",
  "panelr",
  "tigris",
  "censusapi", 
  "tidycensus",
  "RColorBrewer",
  "hrbrthemes",
  "viridis", 
  "wesanderson",
  "leaflet", 
  "tmap",
  "mapboxapi",
  "reactable",
  "htmltools"
)
lapply(packages, library, character.only = T)

## PATHS
setwd("~/Projects/public_space")
wd <- getwd()
parks_path <- "/green_space/usa_parks/"
imperv_space_path <- "/impervious_space/"
census_data_path <- "/census"
shp_repo <- "C:/Users/Franc/Documents/Shapefile_Repository"
shp2010_path <- "/2010USA_CensusGeog_Shp"
cbsa_path <- "/tl_2010_us_cbsa10/"
tracts10_path <- "/2010USA_CensusGeog_Shp/nhgis0005_shapefile_tl2010_us_tract_2010/"
metros10_path <- "/2010USA_CensusGeog_Shp/tl_2010_us_cbsa10/"
metdiv_path <- "/tl_2010_us_metdiv10/"
cbg10_path <- "/us_blck_grp_2010/"
places10_path <- "/tl2010_us_place_2010/"

## PARAMETERS
albersea <- 7301  #general Albers Equal Area Conic 
#or Lamberts Conformal Conic
wgs <- 4326

mb_access_token("sk.eyJ1IjoiZnJhbmNpbmVzdGVwaGVucyIsImEiOiJja2ljb3VrczMwdDdhMnhsNjA4Yjh1c2h1In0.WJjq6TysT6zZZnaxsN0s5g",
                overwrite = TRUE)
readRenviron("~/.Renviron")



## SHAPEFILE IMPORTS
cbg10 <- st_read(paste0(shp_repo,
                        shp2010_path,
                        cbg10_path,
                        "US_blck_grp_2010.shp"), 
                 quiet = FALSE)

tracts10 <- st_read(paste0(shp_repo, 
                           tracts10_path,
                           "US_tract_2010.shp"),
                    quiet = F)

metros10 <- st_read(paste0(shp_repo, 
                         metros10_path,
                         "tl_2010_us_cbsa10.shp"),
                  quiet = FALSE)

state_codes <- c(state.abb, "DC")

places <- map_df(state_codes,
                 ~places(state = .x, cb = TRUE)
                )

counties <- map_df(state_codes,
                 ~counties(state = .x, cb = TRUE)
                )

data(fips_codes)


usa_parks <- st_read(paste0(wd,
                            parks_path,
                            'USA Parks.shp'))

## DATA IMPORTS-----------------------------------------------------------------
full_cbg_data_l <- readRDS("all_vars_on_cbg10_LONG.rds")
full_cbg_data_chg_w <- readRDS("chg_vars_on_cbg10_WIDE.rds")
parks_scores <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-22/parks.csv') 
    # The Public Lands Trust Parks Scores
    # https://www.tpl.org/parkserve/downloads
    # https://www.tpl.org/parkscore/about


## FUNCTIONS--------------------------------------------------------------------
compute_area_sqmi <- function(x) { 
  x %>%       
  st_transform(., albersea) %>%
  mutate(
    area = st_area(.),
    area_sqmi = as.numeric(set_units(area, mi^2))
    )
}

post_intersection_cleaning <- function(x) { 
  x %>% 
  mutate(
    intersection_area = st_area(.),
    area_sqmi = as.numeric(set_units(intersection_area, mi^2))
    ) %>%
  group_by(GEOID) %>%
  summarize(parks = n(),
            total_park_area = sum(SQMI),
            total_park_area_sqme = sum(intersection_area),
            total_park_area_sqmi = sum(area_sqmi)
            )  %>%
  st_set_geometry(NULL) 
  }

create_paged_table_view <- function(x) { 
  x %>%       
  left_join(., state_identifiers, by = c("STATEFP" ="state_code")
            ) %>%
  left_join(., places_area %>% select(GEOID, area_sqmi), by = "GEOID") %>%
  mutate(percent_of_land_area = (total_park_area_sqmi/area_sqmi) * 100) %>%
  select(NAME, state, parks, total_park_area_sqmi, percent_of_land_area)
}

```

## Parks Attributes

There are a total of 58,028 parks in the USA Parks dataset. The table below shows the breakdown by type of park space. 85% of the park spaces are owned and maintained by local governments. 


```{r park types}
knitr::kable(usa_parks %>% 
               st_set_geometry(NULL) %>%
               select(FEATTYPE) %>%
               count(FEATTYPE) %>%
               arrange(-n),
             col.names = c("Type of Park", "Freq."),
             caption = "Count of Parks in the U.S.",
             format.args = list(big.mark = ",")
             )

```

```{r projection}
## Projections
usa_parks_prj <- usa_parks %>%
  st_transform(., crs = albersea)
  
```

```{r fips codes set-up}
## State fips codes only
state_identifiers <- fips_codes %>%
  select(state:state_name) %>%
  distinct(.)

```

## Parks by Places {.tabset .tabset-fade}

```{r overlay parks on places, echo=FALSE}
## intersection join
# parks_per_places <- usa_parks_prj %>%
#   st_intersection(., places %>% st_transform(., albersea)
#                   ) %>%
#   post_intersection_cleaning(.) %>%
#   left_join(., places, by = "GEOID")
# saveRDS(parks_per_places, "parks_per_places_2021.rds")
parks_per_places <- readRDS("parks_per_places_2021.rds")

## compute area of places
places_area <- places %>% 
  compute_area_sqmi(.)

```

```{r park park count results}
# rmarkdown::paged_table(parks_per_places %>% 
#   create_paged_table_view(.) %>%
#   arrange(-parks) 
# )
  # 54,083 parks 

parks_per_places_reactable <- reactable(parks_per_places %>% 
  create_paged_table_view(.) %>%
  arrange(-parks) %>% 
    mutate(total_park_area_sqmi = round(total_park_area_sqmi, digits = 2),
           percent_of_land_area = percent(percent_of_land_area, accuracy = 0.01,
                                                scale = 1, suffix = "%" 
                                                 )
           ) %>%
  rename(Name = "NAME",
         State = "state",
         Parks = "parks", 
         'Area (Sq Mi)' = "total_park_area_sqmi",
         'Percent of Land Cover' = "percent_of_land_area"), 
  searchable = TRUE,
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  minRows = 10
  )

div(class = "parks_per_places_reactable",
  div(class = "parks_per_places_reactable-header",
      h3(class = "parks_per_places_reactable-title", "Table 1: Parks per Places"),
     parks_per_places_reactable
  )
)

```


```{r places without parks}
## FIND PLACES WITHOUT PARK SPACE
# rmarkdown::paged_table(places %>% 
#   filter(!GEOID %in% parks_per_places$GEOID) %>%
#   st_set_geometry(NULL) %>% 
#   left_join(., state_identifiers, by = c("STATEFP" ="state_code")
#             ) %>%
#   select(NAME, state)
# )


places_without_parks_reactable <- reactable(places %>% 
  filter(!GEOID %in% parks_per_places$GEOID) %>%
  st_set_geometry(NULL) %>% 
  left_join(., state_identifiers, by = c("STATEFP" ="state_code")
            ) %>%
  select(Name = "NAME", State = "state"), 
  searchable = TRUE, 
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  minRows = 10)


div(class = "places_without_parks_reactable",
  div(class = "places_without_parks_reactable-header",
      h3(class = "places_without_parks_reactable-title", "Table 2: Places without Parks"),
     places_without_parks_reactable
  )
)

```


### Chicago

Chicago has the most parks. The number of green-ways, (i.e., green areas between major roadways), particularly on the western side of the city  is striking.

```{r extract chicago and its parks}
chicago <- places %>%
  filter(NAME == "Chicago") %>%
  compute_area_sqmi(.)

chicago_parks <- usa_parks_prj %>% 
  st_intersection(., chicago %>% st_transform(., albersea)
                  ) %>%
  mutate(
    intersection_area = st_area(.),
    area_sqmi = as.numeric(set_units(intersection_area, mi^2))
    )
  
leaflet() %>% 
  addTiles() %>%
  addPolygons(
    data = chicago_parks %>% st_transform(., wgs),
    label = ~NAME,
    fillColor = "green",
    weight = 2,
    opacity = 1,
    color = "white",
    fillOpacity = 0.7
  )

```

Although there are many parks in Chicago, they tend to be small in size. The average park area is 0.03 square miles. The largest park is 1.27 square miles. In total, park space makes up 17.05 square miles in Chicago, which is approximately 7% of the city's land area.   

```{r chicago park size}
summary(chicago_parks$area_sqmi)

```


Most of Chicago's parks are local. 2 are county and 3 are regional. 

```{r chicago types of parks}
knitr::kable(chicago_parks %>% 
               st_set_geometry(NULL) %>%
               select(FEATTYPE) %>%
               count(FEATTYPE) %>%
               arrange(-n),
             col.names = c("Type of Park", "Freq."),
             caption = "Count of Parks in Chicago.",
             format.args = list(big.mark = ",")
             )

```


### Philadelphia

```{r extract philly and its parks}
philly <- places %>%
  filter(NAME == "Philadelphia" & STATEFP == "42") %>%
  compute_area_sqmi(.)

philly_parks <- usa_parks_prj %>% 
  st_intersection(., philly %>% st_transform(., albersea)
                  ) %>%
  mutate(
    intersection_area = st_area(.),
    area_sqmi = as.numeric(set_units(intersection_area, mi^2))
    )
  
leaflet() %>% 
addMapboxTiles(
    style_id = "streets-v11",
    username = "mapbox"
  ) %>%
  addPolygons(
    data = philly %>% st_transform(., wgs),
    fillColor = "transparent",
    color = "black"
  ) %>%
  addPolygons(
    data = philly_parks %>% st_transform(., wgs),
    label = ~NAME,
    fillColor = "green",
    weight = 2,
    opacity = 1,
    color = "white",
    fillOpacity = 0.7
  )

```

### Hialeah 

Hialeah is among the top 100 cities by population size as of 2010. Among the top 100 cities, Hialeah has the lowest amount of park area. There are 17 parks in Hialeah. All of these parks are locally maintained and owned. 

```{r extract hialeah and its parks}
hialeah <- places %>%
  filter(NAME == "Hialeah") %>%
  compute_area_sqmi(.)

hialeah_parks <- usa_parks_prj %>% 
  st_intersection(., hialeah %>% st_transform(., albersea)
                  ) %>%
  mutate(
    intersection_area = st_area(.),
    area_sqmi = as.numeric(set_units(intersection_area, mi^2))
    )
  
leaflet() %>% 
  addTiles() %>%
  addPolygons(
    data = hialeah %>% st_transform(., wgs),
    fillColor = "transparent",
    color = "black"
  ) %>% 
  addPolygons(
    data = hialeah_parks %>% st_transform(., wgs),
    label = ~NAME,
    fillColor = "green",
    weight = 2,
    opacity = 1,
    color = "white",
    fillOpacity = 0.7
  )
  

```

The parks cover small amounts of area. The average park size in Hialeah is 0.01 square miles, and the largest park spans about 0.04 miles. 

```{r hialeah park area}
summary(hialeah_parks$area_sqmi)

```


### Eau Claire 

Eau Claire, Wisconsin is another city with very low park coverage. 


```{r extract Eau Claire and parks}
eau_claire <- places %>%
  filter(NAME == "Eau Claire" & STATEFP == "55") %>%
  compute_area_sqmi(.)

eau_claire_parks <- usa_parks_prj %>% 
  st_intersection(., eau_claire %>% st_transform(., albersea)
                  ) %>%
  mutate(
    intersection_area = st_area(.),
    area_sqmi = as.numeric(set_units(intersection_area, mi^2))
    )

leaflet() %>% 
  addTiles() %>%
  addPolygons(
    data = eau_claire %>% st_transform(., wgs),
    fillColor = "transparent",
    color = "black"
  ) %>% 
  addPolygons(
    data = eau_claire_parks %>% st_transform(., wgs),
    label = ~NAME,
    fillColor = "green",
    weight = 2,
    opacity = 1,
    color = "white",
    fillOpacity = 0.7
  )

```


## Parks by County

```{r overlay parks on counties}
## Create parks per county dataset 
# parks_per_county <-  usa_parks_prj %>% 
#   st_intersection(., counties %>% st_transform(., albersea)
#                   ) %>%
#   post_intersection_cleaning(.) %>%
#   left_join(., counties, by = "GEOID")
# saveRDS(parks_per_county, "parks_per_county_2021.rds")
parks_per_county <- readRDS("parks_per_county_2021.rds")


## compute area of places
counties_area <- counties %>% 
  compute_area_sqmi(.)

```


```{r parks per county table}
#61,569 park count
## create table
parks_per_county_reactable <- reactable(parks_per_county %>% 
  create_paged_table_view(.) %>% 
    mutate(total_park_area_sqmi = round(total_park_area_sqmi, digits = 2),
           percent_of_land_area = percent(percent_of_land_area, accuracy = 0.01,
                                                scale = 1, suffix = "%" 
                                                 )
           ) %>%
  rename(County = "NAME",
         State = "state",
         Parks = "parks", 
         'Area (Sq Mi)' = "total_park_area_sqmi",
         'Percent of Land Cover' = "percent_of_land_area"), 
  searchable = TRUE,
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  minRows = 10
  )

div(class = "parks_per_county_reactable",
  div(class = "parks_per_county_reactable-header",
      h3(class = "parks_per_county_reactable-title", "Table 3: Parks per County"),
     parks_per_county_reactable
  )
)


```

```{r find counties without park spaces}
# FIND COUNTIES WITHOUT PARK SPACE
counties_without_parks_reactable <- reactable(counties %>% 
  filter(!GEOID %in% parks_per_county$GEOID) %>%
  st_set_geometry(NULL) %>% 
  left_join(., state_identifiers, by = c("STATEFP" ="state_code")
            ) %>%
  select(County = "NAME", State = "state"), 
  searchable = TRUE, 
  filterable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  minRows = 10)


div(class = "counties_without_parks_reactable",
  div(class = "counties_without_parks_reactable-header",
      h3(class = "counties_without_parks_reactable-title", "Table 2: Counties without Parks"),
     counties_without_parks_reactable
  )
)

```


## Parks by Metros

```{r overlay parks of metros}
## Create parks by metros dataset
# parks_per_metro <-  usa_parks_prj %>%
#   st_intersection(., metros10 %>% st_transform(., albersea)
#                   ) %>%
#   mutate(
#     intersection_area = st_area(.),
#     area_sqmi = as.numeric(set_units(intersection_area, mi^2))
#     ) %>%
#   group_by(GEOID10) %>%
#   summarize(parks = n(),
#             total_park_area = sum(SQMI),
#             total_park_area_sqme = sum(intersection_area),
#             total_park_area_sqmi = sum(area_sqmi)
#             )  %>%
#   st_set_geometry(NULL) %>%
#   left_join(., metros10, by = "GEOID10")
# saveRDS(parks_per_metro, "parks_per_metro_2021.rds")
parks_per_metro <- readRDS("parks_per_metro_2021.rds")

```

```{r parks per metros intersection}
##st_intersection version
parks_per_metro %>% 
  select(parks, total_park_area_sqmi, NAME10, GEOID10) %>%
  arrange(-parks)


# FIND METROS/MICROS WITHOUT PARK SPACE
metros10 %>%
  filter(!GEOID10 %in% parks_per_metro$GEOID10) %>% 
  st_set_geometry(NULL) %>%
  select(GEOID10:NAMELSAD10)

```

